Does freshwater connectivity influence phosphorus retention in lakes?

### 2019-02-08 manuscript/manuscript.Rmd
enable showing ref dois
insert zenodo doi

# Place eg a DOI URL or CRAN Package URL here
doi_footer: "https://doi.org/ZenodoDOI"

@@

# Optional: Bibliography
bibliography: pinp
biblio-style: bioscience

@@

We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively \citep{R-streamnet, R-nhdR}. The algorithms in the `streamnet` package use the `sf` R package \citep{pebesma2018} as well as the `v.net` and `v.stream.order` modules \citep{jasiewiczNewGRASSGIS2011} included in GRASS GIS \citep{GRASS_GIS_software}. All processed connectivity data and code are available at [Zenodo DOI].

>>>>

# Place eg a DOI URL or CRAN Package URL here
doi_footer: "https://doi.org/10.5281/zenodo.2554212"

@@

# Optional: Bibliography
bibliography: pinp
biblio-style: elsarticle-harv

@@

We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively \citep{R-streamnet, R-nhdR}. The algorithms in the `streamnet` package use the `sf` R package \citep{pebesma2018} as well as the `v.net` and `v.stream.order` modules \citep{jasiewiczNewGRASSGIS2011} included in GRASS GIS \citep{GRASS_GIS_software}. All processed connectivity data and code are available at https://doi.org/10.5281/zenodo.2554212.
